### 2015-12-29 article/main.tex
[add] template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Detection of design pattern : A systematic mapping study}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Pierre Gerard, Alexandre Saint-Louis Fortier, Badr Mai and Houari Sahraoui \\
Département IRO \\
Université de Montréal, Montreal, Canada \\
\{gerardpi,Unknown,Unknown,sahraouh\}@iro.umontreal.ca
% <-this % stops a space
%\thanks{*This work was not supported by any organization}% <-this % stops a space
%\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
 %       University of Twente, 7500 AE Enschede, The Netherlands
  %      {\tt\small h.kwakernaak at papercept.net}}%
%\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
   %     Dayton, OH 45435, USA
    %    {\tt\small p.misra at ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Abstract goes here

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

Introduction goes here

\section{SYSTEMATIC MAPPING PROCESS}

\subsection{subsection1}

subsection

\section{SELECTION PROCESS RESULT}

selection process goes here

Exemple d'image

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

\section{CONCLUSIONS}

A conclusion section

\addtolength{\textheight}{-12cm}

% This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}

Acknowledgement

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.

\end{thebibliography}

\end{document}

### 2015-12-29 article/main.tex
petit ajout sur le process

@@
 Introduction goes here
+% pourquoi la detection
+
+% pourquoi ce systematic mapping
 
@@
 
-\subsection{subsection1}
+In this section, we discuss step by step how we conducted our systematic mapping study. We have followed the process defined by Petersen et al \cite{c1}.
 
-subsection
+\subsection{Research question}
+
+The main goal of this paper is to determine the quantity and trends of research in design pattern detection and the quality of proposed detection methods.
+\begin{itemize}
+	\item \textbf{RQ1} : How mature is research on the subject of design pattern detection ?
+	\item \textbf{RQ2} : What methods of design pattern detection are used ?
+\end{itemize}
+
+\subsection{Data source and queries}
+
+We decided to query only one database, Scopus \cite{c2}, that claimed to be the largest abstract and citation database of peer-reviewed literature.
+It indeed index the main Computer Science databases : Springer, IEEE, ACM and others.
+The main advantage of doing so is that one could easily export result of an important number of publication from Scopus.
+
+From the two research question we tried to maximise the number of publication found on the subject.
+To achieve that purpose we used for the query a disjonction of thesaurus for detection on their respective contracted form : detect*, recogni* and ident*.
+We have then added to the query a disjonction of pattern and motif.
+We have limited the query to the abstract, the title, and keywords of each article.
+
+We have limited our research to the year between 2000 and 2015 included.
+
+We have also limited our research to the field of computer science and engineering.
+
+The query resulted of a total of 403 articles. In those articles, we found two duplicates that we have immediately removed from the result.
+
+\subsection{Screening}
+
+After having queried the database, we exported results found and process to screening.
+
+% par paire de deux et resolve conflict
+
+The aim of screening is to select papers relevant to design pattern detection. For that purpose, we used an exclusion scheme containing four criteria :
+
+\begin{enumerate}
+	\item \textbf{Not a contribution in software engineering} : %explaination ,
+	\item \textbf{Not a full conference or research paper},
+	\item \textbf{Not about software design pattern} : %explaination,
+	\item \textbf{The main contribution of the paper is not about detection of design pattern} : %explaination
+\end{enumerate}
+
+If in article matched more than one criteria, we assigned the lowest criteria to him.
+
+% kappa de cohen
+
+\subsection{Classification scheme}
+
+% comment on l'a choisit
+
+% explication pour chaque catégorie
+\begin{itemize}
+	\item \textbf{Detection strategy}
+	\item \textbf{Language generality}
+	\item \textbf{Analysis type}
+	\item \textbf{Validation method}
+	\item \textbf{Detection Level}
+	\item \textbf{Detected pattern types}
+	\item \textbf{Pattern detection generality}
+\end{itemize}
+
+\subsection{Systematic map}
 
 \section{SELECTION PROCESS RESULT}
-
-selection process goes here
-
-Exemple d'image
-
-   \begin{figure}[thpb]
-      \centering
-      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
-}}
-      %\includegraphics[scale=1.0]{figurefile}
-      \caption{Inductance of oscillation winding on amorphous
-       magnetic core versus DC bias magnetic field}
-      \label{figurelabel}
-   \end{figure}
 
@@
 
-\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
-\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.
+\bibitem{c1} K.
+Petersen, R.
+Feldt, S.
+Mujtaba, and M.
+Mattsson, “Systematic mapping studies in software engineering,” in Proc.
+of the 12th Int.
+Conf.
+on Eval.
+and Asses.
+in Soft.
+Eng., ser.
+EASE’08.
+Swinton, UK, UK: British Computer Society, 2008.
+
+\bibitem{c2} www.scopus.com
 

### 2015-12-29 article/main.tex
petit ajout sur le process

@@
 
-% par paire de deux et resolve conflict
+This process was done by pair.
+For each article, we check that the result was the same for each individual in the pair.
+In the case of difference, we first talk about it to find common ground, then if the conflict was not resolved, we asked a senior researcher for a final decision.
 
@@
 \begin{enumerate}
-	\item \textbf{Not a contribution in software engineering} : %explaination ,
+	\item \textbf{Not a contribution in software engineering} : this criteria also exclude articles that are not more than an use case of software engineering,
 	\item \textbf{Not a full conference or research paper},
-	\item \textbf{Not about software design pattern} : %explaination,
-	\item \textbf{The main contribution of the paper is not about detection of design pattern} : %explaination
+	\item \textbf{Not about software design pattern} : this criteria exclude articles where the main contribution is not about design pattern as defined in the Gang Of Four ,
+	\item \textbf{The main contribution of the paper is not about detection of design pattern}.
 \end{enumerate}
@@
 
-% kappa de cohen
+We were three author to work on the screening, we therefore created three pair of author including on average 135 articles per pair.
+
+The inter-rater agreement cohen's kappa gave us the following result:
+% citation needed
+
+\begin{center}
+  \begin{tabular}{ | l | c | }
+    \hline
+    Group 1 & 0.88 \\ \hline
+    Group 2 & 0.66 \\ \hline
+    Group 3 & 0.91 \\
+    \hline
+  \end{tabular}
+\end{center}
+
+It is usually said that a cohen's kappa coefficient of more than 0.7 indicate a good agreeement.% citation needed
 
@@
 
-% comment on l'a choisit
+To determine a relevant classification scheme we mainly used three things.
+The first was our general knowledge of the field on the subject and the matter ensuing.
+The second was the information extracted during the screening process that allowed us to identify the most important classification items.
+The last one was advices on which are the important point from a senior researcher who used to work on design pattern detection techniques.
 
+All of that leaded us to seven main categories.
 % explication pour chaque catégorie
 \begin{itemize}
-	\item \textbf{Detection strategy}
-	\item \textbf{Language generality}
+	\item \textbf{Detection strategy} : 
+	\item \textbf{Language generality} : This specifies if the detection is langage dependent or independent.
 	\item \textbf{Analysis type}

### 2015-12-30 article/main.tex
petit ajout sur le process

@@
 All of that leaded us to seven main categories.
-% explication pour chaque catégorie
+
 \begin{itemize}
-	\item \textbf{Detection strategy} : 
-	\item \textbf{Language generality} : This specifies if the detection is langage dependent or independent.
-	\item \textbf{Analysis type}
-	\item \textbf{Validation method}
-	\item \textbf{Detection Level}
-	\item \textbf{Detected pattern types}
-	\item \textbf{Pattern detection generality}
+	\item \textbf{Detection strategy} : This determine the means on which the detection is based.
+It could include Artificial intelligence, machine learning, graph, metrics, logic, automata, instrumentation, pattern matching or others techniques.
+	\item \textbf{Language generality} : This specifies if the detection is langage dependent or independent,
+	\item \textbf{Analysis type} : This determine if a detection techniques use a static, dynamic or hybrid approach.
+	\item \textbf{Validation method} : This specifies the type of scientific validation methods the article's authors used for a detection method.
+	\item \textbf{Detection Level} : This define on which level the detection method work : execution, source and model. It could be more than one level for a single method of detection.
+	\item \textbf{Detected pattern types} : This characterizes the type of design pattern a specific detection method can manage.
+	\item \textbf{Pattern detection generality} : This determine if a method is made to detect a single pattern or more than one pattern.
 \end{itemize}
@@
 \subsection{Systematic map}
+
+%todo
 

### 2015-12-31 article/main.tex
Corrections, diagrams et a little more

--- 2015-12-29 article/main.tex
@@
 %\usepackage{graphics} % for pdf, bitmapped graphics files
+\usepackage{graphicx} % for png files
+\graphicspath{{img/}}
 %\usepackage{epsfig} % for postscript graphics files
@@
 
-\author{Pierre Gerard, Alexandre Saint-Louis Fortier, Badr Mai and Houari Sahraoui \\
+\author{Pierre Gerard, Alexandre St-Louis Fortier, Badr Mai and Houari Sahraoui \\
 Département IRO \\
 Université de Montréal, Montreal, Canada \\
-\{gerardpi,Unknown,Unknown,sahraouh\}@iro.umontreal.ca
+\{gerardpi,stlouial,sahraouh\}@iro.umontreal.ca
 % <-this % stops a space
@@
 
-Abstract goes here
+% Place holder
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+In pulvinar dui eget dignissim congue.
+Aenean interdum orci arcu, non varius nibh condimentum eu.
+Ut eget purus et purus pharetra egestas.
+Sed nec convallis lorem.
+Mauris fringilla velit est, elementum tincidunt lorem hendrerit ac.
+Vivamus et lorem nisi.
+Maecenas interdum diam id turpis aliquet lacinia.
+
+Morbi rutrum tortor volutpat lacus lobortis interdum.
+Nam at mauris tristique, vulputate tortor non, egestas ex.
+Ut mauris libero, egestas at lacus sit amet, volutpat volutpat sapien.
+Quisque aliquet diam maximus lorem laoreet accumsan.
+Integer eleifend magna at nunc dapibus bibendum.
+Nam sagittis velit quis neque rhoncus, eget venenatis ante suscipit.
+Cras condimentum quam justo, quis pharetra nisi porta at.
+Sed sed ultricies dui.
+Sed id facilisis metus.
+
+Maecenas feugiat augue purus, id interdum tellus sagittis at.
+Donec a orci sem.
+Aenean non elit maximus, fermentum odio et, mattis neque.
+Sed interdum in odio at egestas.
+Proin vel mi at elit congue lacinia et eu lectus.
+Praesent at rhoncus ante.
+Sed pulvinar tortor quis congue sagittis.
+Quisque tortor mi, semper vel rhoncus eu, sollicitudin et nibh.
 
@@
 
-Introduction goes here
+% Design patterns are a
+
+Design partterns are best pratice to recurring problems proposed by the Gang
+of Four in their seminal book.
+
+(Some study author) have been able to show that the presence of design patterns
+can help one better understand a piece of software.
+
+Detection of design patterns in software has been a relatively active research
+interest of the past decade in software engineering.
+Proposed methods of automatic detection aims in part to facilitate the work of
+developpers in understanding a piece of software through reverse engineering.
+
+However, no studies have been conducted to analyse the trends of the field.
+
 % pourquoi la detection
@@
 
-In this section, we discuss step by step how we conducted our systematic mapping study. We have followed the process defined by Petersen et al \cite{c1}.
+In this section, we discuss step by step how we conducted our systematic
+mapping study.
+We have followed the process defined by Petersen et al \cite{c1}.
 
@@
 
-The main goal of this paper is to determine the quantity and trends of research in design pattern detection and the quality of proposed detection methods.
+The main goal of this paper is to determine the quantity and trends of research
+in design pattern detection and the quality of proposed detection methods.
+% Our classification scheme doesn't really allow us to take any position
+% relative to the quality of the methods. At most, it provide a sensible
+% evaluation of the field
+
 \begin{itemize}
@@
 
-We decided to query only one database, Scopus \cite{c2}, that claimed to be the largest abstract and citation database of peer-reviewed literature.
-It indeed index the main Computer Science databases : Springer, IEEE, ACM and others.
-The main advantage of doing so is that one could easily export result of an important number of publication from Scopus.
+We decided to query only one database, Scopus \cite{c2}, that claims to be the
+largest abstract and citation database of peer-reviewed literature.
+It indexes the main Computer Science databases : Springer, IEEE, ACM and
+others.
+The main advantage of using Scopus is that it provides a functionnality to
+export the result of a search query on its database.
+Some of those exported results would not have been easily obtainable on some
+publishers search engines that do not provide an export functionnality.
+Consequently, Scopus was used mostly as a Search and Export portal over the
+relevant publications, greatly reducing the effort needed to extract the
+original articles set. 
+% TODO: Original articles set <- better wording?!
 
-From the two research question we tried to maximise the number of publication found on the subject.
-To achieve that purpose we used for the query a disjonction of thesaurus for detection on their respective contracted form : detect*, recogni* and ident*.
-We have then added to the query a disjonction of pattern and motif.
-We have limited the query to the abstract, the title, and keywords of each article.
+From the two research questions we tried to maximise the number of publications
+found on the subject.
+% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
+% doesn't make any sense.
+To achieve that purpose we used for the query a disjonction of thesaurus for
+\textit{detection} on their respective contracted form : \textit{detect*},
+\textit{recogni*} and \textit{ident*}.
+We have then added to the query a disjonction of \textit{pattern} and \textit{motif}.
+The query was limitied to the abstract, the title, and keywords of each article.
+% Do we like oxford comma?
 
-We have limited our research to the year between 2000 and 2015 included.
+To limit the scope of our research only the articles published between the years
+2000 and 2015 have been included.
 
-We have also limited our research to the field of computer science and engineering.
+% This sentence is not necessary... It is evident that we excluded other domains.
+We have also limited our research to the field of computer science and
+engineering.
 
-The query resulted of a total of 403 articles. In those articles, we found two duplicates that we have immediately removed from the result.
+The query resulted in a total of 403 articles.
+Of those articles, we found two duplicates that were immediately removed from
+the set of articles to analyse which brings down the number of articles for
+screening to 401.
 
@@
 
-After having queried the database, we exported results found and process to screening.
+% Problem with that sentence
+After having queried the database, we exported the results found and process to
+screening.
 
 This process was done by pair.
-For each article, we check that the result was the same for each individual in the pair.
-In the case of difference, we first talk about it to find common ground, then if the conflict was not resolved, we asked a senior researcher for a final decision.
+For each article, we check that the result was the same for each individual in
+the pair.
+In the case of difference, we first talk about it to find common ground, then
+if the conflict was not resolved, we asked a senior researcher for a final
+decision.
 
-The aim of screening is to select papers relevant to design pattern detection. For that purpose, we used an exclusion scheme containing four criteria :
+The aim of screening is to select papers relevant to design pattern detection.
+For that purpose, we used an exclusion scheme containing four criteria:
 
 \begin{enumerate}
-	\item \textbf{Not a contribution in software engineering} : this criteria also exclude articles that are not more than an use case of software engineering,
+  \item \textbf{Not a contribution in software engineering}: 
+    This criterion was used to exclude articles not relevant to the domain and
+    software engineering articles that are nothing more than mere use case
+    reports.
   \item \textbf{Not a full conference or research paper},
-	\item \textbf{Not about software design pattern} : this criteria exclude articles where the main contribution is not about design pattern as defined in the Gang Of Four ,
-	\item \textbf{The main contribution of the paper is not about detection of design pattern}.
+    This criterion was used to exclude small
+  \item \textbf{Not about software design pattern}:
+    This criterion excludes articles where the main contribution is not about
+    design pattern as defined in by the Gang of Four ,
+  \item \textbf{The main contribution of the paper is not about a method of detecting design patterns}:
+    This criterion was used to exclude benchmarks and other analysis whose main
+    purposes are not a method of design pattern detection.
 \end{enumerate}
 
-If in article matched more than one criteria, we assigned the lowest criteria to him.
+If in article matched more than one criteria, we assigned the lowest criteria
+to it.
 
-We were three author to work on the screening, we therefore created three pair of author including on average 135 articles per pair.
+We were three author to work on the screening, we therefore created three pair
+of author including on average 135 articles per pair.
 
-The inter-rater agreement cohen's kappa gave us the following result:
+The inter-rater agreement Cohen's kappa gave us the following result:
 % citation needed
@@
 \begin{center}
-  \begin{tabular}{ | l | c | }
-    \hline
-    Group 1 & 0.88 \\ \hline
-    Group 2 & 0.66 \\ \hline
-    Group 3 & 0.91 \\
-    \hline
+  \begin{tabular}{ lcc }
+    \bf Group & \bf \# of articles & \bf Cohen's kappa \\
+    1 & ??? & 0.88 \\
+    2 & ??? & 0.66 \\
+    3 & ??? & 0.91 \\
   \end{tabular}
@@
 
-It is usually said that a cohen's kappa coefficient of more than 0.7 indicate a good agreeement.% citation needed
+It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
+a good agreeement.% citation needed
 
@@
 To determine a relevant classification scheme we mainly used three things.
-The first was our general knowledge of the field on the subject and the matter ensuing.
-The second was the information extracted during the screening process that allowed us to identify the most important classification items.
-The last one was advices on which are the important point from a senior researcher who used to work on design pattern detection techniques.
+The first was our general knowledge of the field on the subject and the matter
+ensuing.
+The second was the information extracted during the screening process that
+allowed us to identify the most important classification items.
+The last one was advices on which are the important point from a senior
+researcher who used to work on design pattern detection techniques.
 
 All of that leaded us to seven main categories.
-% explication pour chaque catégorie
+
 \begin{itemize}
-	\item \textbf{Detection strategy} : 
-	\item \textbf{Language generality} : This specifies if the detection is langage dependent or independent.
-	\item \textbf{Analysis type}
-	\item \textbf{Validation method}
-	\item \textbf{Detection Level}
-	\item \textbf{Detected pattern types}
-	\item \textbf{Pattern detection generality}
+  \item Detection strategy:
+    This determine the means on which the detection is based.
+    Possible values: Artificial intelligence, Logic/Formalisation, Graph,
+    Metric, Automata, Instrumentation/profiling and Others.
+
+  \item Language dependance
+    This category aims to classify detection methods on wether it is dependant
+    on the language or not. 
+    Possible values: Dependant or Independant
+% This  specifies if the detection is langage dependent or independent,
+
+  \item Analysis type
+    This determine if a detection techniques use a static, dynamic or hybrid
+    approach.
+    Possible values: Static, Dynamic and Hybrid.
+
+  \item Validation method:
+    This specifies the type of scientific validation methods the article's 
+    authors used for a detection method.
+    Possible values: Benchmark, Case study, Experiment, Survey, Other and
+    None.
+
+  \item{Detection Level}
+    This define on which level the detection method work : execution, source
+    and model.
+    It could be more than one level for a single method of detection.
+    Possible values: Execution, Source and Model.
+
+  \item Detected pattern types :
+    This characterizes the type of design pattern a specific detection method
+    can manage.
+    The possible values for this category are Creationnal, Behavioural,
+    Structural and Not specified.
+
+  \item Pattern detection generality :
+    This determine if a method is made to detect a single pattern or more than
+    one pattern.
+    Possible values: Specific, General.
 \end{itemize}
@@
 
+% Need result table
+
+\subsubsection{Year distribution}
+% Need to change the title for this graphic
+
+\begin{center}
+\includegraphics[scale=0.75]{articles_by_years.png}
+\end{center}
+
+\subsubsection{Venue Distribution}
+% Need a graphic for article by publishers.
+
+\subsubsection{Detection Strategy}
+
+\begin{center}
+\includegraphics[scale=0.75]{detection_strategy.png}
+\end{center}
+
+\subsubsection{Analysis Type}
+
+Design pattern detection can be done either statically or dynamically.
+
+\begin{center}
+\includegraphics[scale=0.75]{analysis_type.png}
+\end{center}
+
+\subsubsection{Detected Pattern Types}
+
+The Gang of Four identified three design pattern types: creationnal,
+behavioural and structural patterns.
+Due to the nature of each pattern types, it is usally aknowledged that
+structural patterns should be easier to detect than behavioural patterns and
+that the later are easier than creationnal patterns (citation needed). 
+It was expected that this ordering would appear in the number of articles
+associated with each pattern types. 
+However, we can see that the detection of behavioural patterns has been the
+subject of more articles than the two others.
+
+\begin{center}
+  \includegraphics[scale=0.65]{pattern_types.png}
+\end{center}
+
+This can be explained either by the fact that structural design patterns
+detection is considered as an easy problem, thus less likely to be the main
+focus of a research papers or by the possibility is that behavioural design
+patterns are in fact easier to detect than structural ones.
+However, we believe the first possibilty to be more likely.
+
+\subsubsection{Language dependance}
+
+\begin{center}
+\includegraphics[scale=0.75]{language_generality.png}
+\end{center}
+
+\subsubsection{Detection Level}
+
+\begin{center}
+\includegraphics[scale=0.75]{detection_level.png}
+\end{center}
+
+\subsubsection{Detection generality}
+
+\begin{center}
+\includegraphics[scale=0.75]{detection_generality.png}
+\end{center}
+
+\subsubsection{Validation Methods}
+
+\begin{center}
+\includegraphics[scale=0.75]{validation_method.png}
+\end{center}
+
+\subsubsection{Detected pattern types according to analysis type}
+% Need graphics
+
+%todo
+
 \section{SELECTION PROCESS RESULT}
+
+DATA
+
+\section{Study limitations}
+
+\subsection{Selection Bias}
+
+A possible limitation of our studies is the selection of a unique source for 
+the articles in Scopus.
+This was done to facilitate our work in the extraction of relevant articles
+since Scopus offers to export the results of a search query on its database.
+It has been assumed that it does an exhaustive indexing of the journals
+and conferences it references and that those sources includes most of the
+relevant publications that covers software design pattern detection.
+To mitigate the possibility of missing relevant articles we made sure that
+Scopus indexes the big venues of software engineering (ACM, Springer, IEEE, and
+???).
+
+\subsection{Screening}
+
+There is a possibility for relevant articles to have been excluded at the
+screening level due to a non representative title and abstract.
+We believe the possibility to be unlikely since each article were screened by
+two reviewers and that if the article had a possibly misleading title, it would
+be rejected after a complete reading done before the classification phase.
+
+As it can be seen with Cohen's kappa coefficient of the second screening group,
+there were some disagreement related to the inclusion or the exclusion of some
+articles.
+Most of those disagreement comes from different views of what constitute a
+software engineering papers and the fact that many fields have adopted the
+concept of design patterns.
+Even if the Cohen's kappa coefficient can be considered somewhat low for the
+second group, we are confident with our screening since most disagreement have
+been resolved by an experienced researcher in the field if a pair of reviewers
+couldn't reach a consensus.
+
+\subsection{Classification}
+
+At first, we defined the detection level to be a disjoint classification category.
+However during the classification phase of our study, we stumbled upon unfoseen cases
+where the detection was done at two levels. We had to change the classification
+scheme to allow those cases.
+
+\section{Related works}
+
+So far, no other comparable studies has been done on the field of design pattern
+recognition.
+
+(article on method validation) have identified a problem in the evaluation of design
+pattern detection methods. This problem has been observed in our evaluation of the
+domain in that most articles evaluates their algorithms with case studies that are
+hardly comparable.
 

### 2015-12-31 article/main.tex
modified:   article/main.tex abstract

@@
 % Place holder
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-In pulvinar dui eget dignissim congue.
-Aenean interdum orci arcu, non varius nibh condimentum eu.
-Ut eget purus et purus pharetra egestas.
-Sed nec convallis lorem.
-Mauris fringilla velit est, elementum tincidunt lorem hendrerit ac.
-Vivamus et lorem nisi.
-Maecenas interdum diam id turpis aliquet lacinia.
-
-Morbi rutrum tortor volutpat lacus lobortis interdum.
-Nam at mauris tristique, vulputate tortor non, egestas ex.
-Ut mauris libero, egestas at lacus sit amet, volutpat volutpat sapien.
-Quisque aliquet diam maximus lorem laoreet accumsan.
-Integer eleifend magna at nunc dapibus bibendum.
-Nam sagittis velit quis neque rhoncus, eget venenatis ante suscipit.
-Cras condimentum quam justo, quis pharetra nisi porta at.
-Sed sed ultricies dui.
-Sed id facilisis metus.
-
-Maecenas feugiat augue purus, id interdum tellus sagittis at.
-Donec a orci sem.
-Aenean non elit maximus, fermentum odio et, mattis neque.
-Sed interdum in odio at egestas.
-Proin vel mi at elit congue lacinia et eu lectus.
-Praesent at rhoncus ante.
-Sed pulvinar tortor quis congue sagittis.
-Quisque tortor mi, semper vel rhoncus eu, sollicitudin et nibh.
+Design patterns are important because they help solving recurring design problems in software engineering.
+The identification of those patterns can be helpful to maintain and understand the code especially in large systems.
+Interest in design patterns detection has grown in the last decade.Despite the huge interest given to design patterns detection, there is no reliable or formal method for this matter.
+We conducted a systematic mapping study on design patterns detection by querying multiple sources to get articles that are relevant to our study. 403 articles between 2000 and 2015 were considered.
+The main purpose of the study is to know which methods and techniques are used to detect design patterns.
+The result help us understand how those techniques work and which type of pattern is detected the most.
 

### 2015-12-31 article/main.tex
modified:   article/main.tex

@@
 
-% Need result table
+\includegraphics[scale=0.75]{flux.png}
 
@@
 \subsubsection{Language dependance}
+The majority of techniques are language dependant and the most used 
+languages are Java and C++
 
@@
 
+But those detection methods can be easily converted to other languages
+just by modifying the font-end.
+
 \subsubsection{Detection Level}
-
+We found out that almost all of design patterns detection methods 
+identify the patterns on a source code level, though, the detection could
+be done on multiple levels.
 \begin{center}

### 2015-12-31 article/main.tex
modified:   article/main.tex
modified:   main.tex
Data table

--- 2015-12-31 article/main.tex
@@
 \graphicspath{{img/}}
+\usepackage{multirow}
 %\usepackage{epsfig} % for postscript graphics files
@@
 
-Design partterns are best pratice to recurring problems proposed by the Gang
-of Four in their seminal book.
+Design partterns are best pratices proposed by the Gang of Four in their seminal
+book to recurring design problems.
 
-(Some study author) have been able to show that the presence of design patterns
-can help one better understand a piece of software.
+(Some study author) have been able to show that the presence of design patterns,
+if correctly presented, can help one better understand a piece of software
+[citation needed].
+It is therefore desirable to be able to automatically extract those design
+and present them in a digestible format.
 
@@
 
-However, no studies have been conducted to analyse the trends of the field.
+However, design pattern detection tools are still not featured in the typical
+programmer toolbox.
+
+No studies have been conducted to analyse the trends of the field.
+
+This paper presents a systematic mapping study on design pattern detection
+methods.
+It is organized as follows: 
+ The first section explains the systematic mapping process
+ The second section analyses
 
@@
 
-% Problem with that sentence
+% Problem with that sentence: "and process"?  Maybe "proceeded" 
 After having queried the database, we exported the results found and process to
@@
     \bf Group & \bf \# of articles & \bf Cohen's kappa \\
+    \hline {}
     1 & ??? & 0.88 \\
@@
 \begin{itemize}
-  \item Detection strategy:
+  \item \textbf{Detection strategy}:
     This determine the means on which the detection is based.
@@
 
-  \item Language dependance
+  \item \textbf{Language dependance}:
     This category aims to classify detection methods on wether it is dependant
@@
 
-  \item Analysis type
+  \item \textbf{Analysis type}:
     This determine if a detection techniques use a static, dynamic or hybrid
@@
 
-  \item Validation method:
+  \item \textbf{Validation method}:
     This specifies the type of scientific validation methods the article's 
@@
 
-  \item{Detection Level}
+  \item \textbf{Detection Level}
     This define on which level the detection method work : execution, source
@@
 
-  \item Detected pattern types :
+  \item \textbf{Detected pattern types}:
     This characterizes the type of design pattern a specific detection method
@@
 
-  \item Pattern detection generality :
+  \item \textbf{Pattern detection generality}:
     This determine if a method is made to detect a single pattern or more than
@@
 
-\subsubsection{Year distribution}
+%todo
+
+\section{SELECTION PROCESS RESULTS}
+
+DATA
+
+\section{STUDY RESULTS}
+
+\begin{center}
+  \begin{tabular}{ lll }
+    \bf Category & \bf Class & \bf \# of articles \\
+    \hline
+    \multirow{7}{*}{Detection Srategy}
+    & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
+    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{22} \\
+    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{15} \\
+    & \multicolumn{1}{l}{Metric}       & \multicolumn{1}{l}{7} \\
+    & \multicolumn{1}{l}{Automata}     & \multicolumn{1}{l}{1} \\
+    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{10} \\
+    & \multicolumn{1}{l}{Pattern Mathching}
+                                       & \multicolumn{1}{l}{8} \\
+    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{23} \\
+    \hline
+    \multirow{2}{*}{\textbf{Language Dependance}}
+    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{Independant}  & \multicolumn{1}{l}{XXX} \\
+    \hline
+    \multirow{3}{*}{\textbf{Analysis Type}}
+    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{XXX} \\
+    \hline
+    multirow{3}{*}{Detection Level}
+    & \multicolumn{1}{l}{Execution}    & \multicolumn{1}{l}{8} \\
+    & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\
+    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{7} \\
+    \hline
+    \multirow{2}{*}{Pattern detection generality}
+    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{XXX} \\
+    \hline
+    \multirow{4}{*}{Detected Pattern Types}
+    & \multicolumn{1}{l}{Creationnal}  & \multicolumn{1}{l}{23} \\
+    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{34} \\
+    & \multicolumn{1}{l}{Behaviour}    & \multicolumn{1}{l}{49} \\
+    & \multicolumn{1}{l}{Other/Not Specified}
+                                       & \multicolumn{1}{l}{17} \\
+    \hline
+    \multirow{6}{*}{Validation Method}
+    & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
+    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{40} \\
+    & \multicolumn{1}{l}{Experiment}   & \multicolumn{1}{l}{8} \\
+    & \multicolumn{1}{l}{Survey}       & \multicolumn{1}{l}{0} \\
+    & \multicolumn{1}{l}{Other}        & \multicolumn{1}{l}{1} \\
+    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{11}
+  \end{tabular}
+\end{center}
+
+\subsection{Yearly distribution}
 % Need to change the title for this graphic
+
+The yearly distribution gives us an interesting picture of the field.
+Interest in design patterns detection technique started in the early
+2000 and that interest is fading away since 2010.
+
+This could indicate either that the field is mature and that research avenues
+have been exhaused, that the field currently hit a roadblock, or that interest
+is fading due to a lack of interest in the need for design pattern detection
+tools.
 
@@
 
-\subsubsection{Venue Distribution}
+\subsection{Publication Venue Distribution}
 % Need a graphic for article by publishers.
 
-\subsubsection{Detection Strategy}
+\subsection{Detection Strategy}
 
-\begin{center}
-\includegraphics[scale=0.75]{detection_strategy.png}
-\end{center}
+Most of the detection strategies used fall either in the 
+\textit{logic/formalisation} or \textit{other} class.
+The first one was probably overly broad since it included any solution using
+inference rules engines, formalisation and semantic web ontologies.
+Surprisingly, the latter strategy was the focus of many articles.
 
-\subsubsection{Analysis Type}
+%\begin{center}
+%\includegraphics[scale=0.75]{detection_strategy.png}
+%\end{center}
+
+\subsection{Analysis Type}
 
@@
 
-\begin{center}
-\includegraphics[scale=0.75]{analysis_type.png}
-\end{center}
+%\begin{center}
+%\includegraphics[scale=0.75]{analysis_type.png}
+%\end{center}
 
-\subsubsection{Detected Pattern Types}
+\subsection{Detected Pattern Types}
 
@@
 
-\begin{center}
-  \includegraphics[scale=0.65]{pattern_types.png}
-\end{center}
+%\begin{center}
+%  \includegraphics[scale=0.65]{pattern_types.png}
+%\end{center}
 
@@
 detection is considered as an easy problem, thus less likely to be the main
-focus of a research papers or by the possibility is that behavioural design
+focus of a research paper or by the possibility is that behavioural design
 patterns are in fact easier to detect than structural ones.
@@
 
-\subsubsection{Language dependance}
+\subsection{Language dependance}
 
-\begin{center}
-\includegraphics[scale=0.75]{language_generality.png}
-\end{center}
+%\begin{center}
+%\includegraphics[scale=0.75]{language_generality.png}
+%\end{center}
 
-\subsubsection{Detection Level}
+\subsection{Detection Level}
 
-\begin{center}
-\includegraphics[scale=0.75]{detection_level.png}
-\end{center}
+%\begin{center}
+%\includegraphics[scale=0.75]{detection_level.png}
+%\end{center}
 
-\subsubsection{Detection generality}
+\subsection{Detection generality}
 
-\begin{center}
-\includegraphics[scale=0.75]{detection_generality.png}
-\end{center}
+This category was used to expose specific pattern detection methods.
+Most papers present a general way to detect design patterns.
 
-\subsubsection{Validation Methods}
+%\begin{center}
+%\includegraphics[scale=0.75]{detection_generality.png}
+%\end{center}
 
-\begin{center}
-\includegraphics[scale=0.75]{validation_method.png}
-\end{center}
+\subsection{Validation Methods}
 
-\subsubsection{Detected pattern types according to analysis type}
+%\begin{center}
+%\includegraphics[scale=0.75]{validation_method.png}
+%\end{center}
+
+\subsection{Detected pattern types according to analysis type}
 % Need graphics
-
-%todo
-
-\section{SELECTION PROCESS RESULT}
-
-DATA
 

### 2015-12-31 article/main.tex

@@
 
-% Need result table
-
 %todo
@@
 \subsection{Language dependance}
+The majority of techniques are language dependant and the most used 
+languages are Java and C++
+
+But those detection methods can be easily converted to other languages
+just by modifying the font-end.
 
@@
 \subsection{Detection Level}
+We found out that almost all of design patterns detection methods 
+identify the patterns on a source code level, though, the detection could
+be done on multiple levels.
 

### 2015-12-31 article/main.tex
modified:   main.tex/correction

@@
 
-Design partterns are best pratices proposed by the Gang of Four in their seminal
+Design patterns are best practices proposed by the Gang of Four in their seminal
 book to recurring design problems.
@@
 Proposed methods of automatic detection aims in part to facilitate the work of
-developpers in understanding a piece of software through reverse engineering.
+developers in understanding a piece of software through reverse engineering.
 
@@
 
-No studies have been conducted to analyse the trends of the field.
+No studies have been conducted to analyze the trends of the field.
 
@@
 others.
-The main advantage of using Scopus is that it provides a functionnality to
+The main advantage of using Scopus is that it provides a functionality to
 export the result of a search query on its database.
 Some of those exported results would not have been easily obtainable on some
-publishers search engines that do not provide an export functionnality.
+publishers search engines that do not provide an export functionality.
 Consequently, Scopus was used mostly as a Search and Export portal over the
@@
 
-From the two research questions we tried to maximise the number of publications
+From the two research questions we tried to maximize the number of publications
 found on the subject.
@@
 % doesn't make any sense.
-To achieve that purpose we used for the query a disjonction of thesaurus for
+To achieve that purpose we used for the query a disjunction of thesaurus for
 \textit{detection} on their respective contracted form : \textit{detect*},
 \textit{recogni*} and \textit{ident*}.
-We have then added to the query a disjonction of \textit{pattern} and \textit{motif}.
-The query was limitied to the abstract, the title, and keywords of each article.
+We have then added to the query a disjunction of \textit{pattern} and \textit{motif}.
+The query was limited to the abstract, the title, and keywords of each article.
 % Do we like oxford comma?
@@
 Of those articles, we found two duplicates that were immediately removed from
-the set of articles to analyse which brings down the number of articles for
+the set of articles to analyze which brings down the number of articles for
 screening to 401.
@@
 It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
-a good agreeement.% citation needed
+a good agreement.% citation needed
 
@@
     This determine the means on which the detection is based.
-    Possible values: Artificial intelligence, Logic/Formalisation, Graph,
+    Possible values: Artificial intelligence, Logic/Formalization, Graph,
     Metric, Automata, Instrumentation/profiling and Others.
 
-  \item \textbf{Language dependance}:
-    This category aims to classify detection methods on wether it is dependant
+  \item \textbf{Language dependence}:
+    This category aims to classify detection methods on whether it is dependent
     on the language or not. 
-    Possible values: Dependant or Independant
+    Possible values: Dependant or Independent
 % This  specifies if the detection is langage dependent or independent,
@@
     can manage.
-    The possible values for this category are Creationnal, Behavioural,
+    The possible values for this category are Creational, Behavioral,
     Structural and Not specified.
@@
     \hline
-    \multirow{7}{*}{Detection Srategy}
+    \multirow{7}{*}{Detection Strategy}
     & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
@@
     & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{10} \\
-    & \multicolumn{1}{l}{Pattern Mathching}
+    & \multicolumn{1}{l}{Pattern Matching}
                                        & \multicolumn{1}{l}{8} \\
@@
     \hline
-    \multirow{2}{*}{\textbf{Language Dependance}}
+    \multirow{2}{*}{\textbf{Language Dependence}}
     & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{XXX} \\
-    & \multicolumn{1}{l}{Independant}  & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{Independent}  & \multicolumn{1}{l}{XXX} \\
     \hline
@@
     \multirow{4}{*}{Detected Pattern Types}
-    & \multicolumn{1}{l}{Creationnal}  & \multicolumn{1}{l}{23} \\
+    & \multicolumn{1}{l}{Creational}  & \multicolumn{1}{l}{23} \\
     & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{34} \\
-    & \multicolumn{1}{l}{Behaviour}    & \multicolumn{1}{l}{49} \\
+    & \multicolumn{1}{l}{Behavior}    & \multicolumn{1}{l}{49} \\
     & \multicolumn{1}{l}{Other/Not Specified}
@@
 This could indicate either that the field is mature and that research avenues
-have been exhaused, that the field currently hit a roadblock, or that interest
+has been satisfied, that the field currently hit a roadblock, or that interest
 is fading due to a lack of interest in the need for design pattern detection
@@
 Most of the detection strategies used fall either in the 
-\textit{logic/formalisation} or \textit{other} class.
+\textit{logic/formalization} or \textit{other} class.
 The first one was probably overly broad since it included any solution using
-inference rules engines, formalisation and semantic web ontologies.
+inference rules engines, formalization and semantic web ontologies.
 Surprisingly, the latter strategy was the focus of many articles.
@@
 
-The Gang of Four identified three design pattern types: creationnal,
-behavioural and structural patterns.
-Due to the nature of each pattern types, it is usally aknowledged that
-structural patterns should be easier to detect than behavioural patterns and
-that the later are easier than creationnal patterns (citation needed). 
+The Gang of Four identified three design pattern types: creational,
+behavioral and structural patterns.
+Due to the nature of each pattern types, it is usually acknowledged that
+structural patterns should be easier to detect than behavioral patterns and
+that the later are easier than creational patterns (citation needed). 
 It was expected that this ordering would appear in the number of articles
 associated with each pattern types. 
-However, we can see that the detection of behavioural patterns has been the
+However, we can see that the detection of behavioral patterns has been the
 subject of more articles than the two others.
@@
 detection is considered as an easy problem, thus less likely to be the main
-focus of a research paper or by the possibility is that behavioural design
+focus of a research paper or by the possibility is that behavioral design
 patterns are in fact easier to detect than structural ones.
-However, we believe the first possibilty to be more likely.
+However, we believe the first possibility to be more likely.
 
-\subsection{Language dependance}
-The majority of techniques are language dependant and the most used 
+\subsection{Language dependence}
+The majority of techniques are language dependent and the most used 
 languages are Java and C++
@@
 
-Acknowledgement
+Acknowledgment
 

### 2015-12-31 article/main.tex
modified:   main.tex

@@
 Université de Montréal, Montreal, Canada \\
-\{gerardpi,stlouial,sahraouh\}@iro.umontreal.ca
+\{gerardpi,stlouial,badr.mai,sahraouh\}@iro.umontreal.ca
 % <-this % stops a space
@@
 The identification of those patterns can be helpful to maintain and understand the code especially in large systems.
-Interest in design patterns detection has grown in the last decade.Despite the huge interest given to design patterns detection, there is no reliable or formal method for this matter.
+Interest in design patterns detection has grown in the last decade.
+Despite the huge interest given to design patterns detection, there is no reliable or formal method for this matter.
 We conducted a systematic mapping study on design patterns detection by querying multiple sources to get articles that are relevant to our study. 403 articles between 2000 and 2015 were considered.
@@
     \hline {}
-    1 & ??? & 0.88 \\
-    2 & ??? & 0.66 \\
-    3 & ??? & 0.91 \\
+    1 & 133 & 0.88 \\
+    2 & 133 & 0.66 \\
+    3 & 134 & 0.91 \\
   \end{tabular}
@@
     \hline
-    \multirow{7}{*}{Detection Strategy}
+    \multirow{7}{*}{\textbf{Detection Strategy}}
     & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
@@
     \multirow{2}{*}{\textbf{Language Dependence}}
-    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{XXX} \\
-    & \multicolumn{1}{l}{Independent}  & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{40} \\
+    & \multicolumn{1}{l}{Independent}  & \multicolumn{1}{l}{20} \\
     \hline
@@
     \hline
-    multirow{3}{*}{Detection Level}
+    \multirow{3}{*}{\textbf{Detection Level}}
     & \multicolumn{1}{l}{Execution}    & \multicolumn{1}{l}{8} \\
@@
     \hline
-    \multirow{2}{*}{Pattern detection generality}
+    \multirow{2}{*}{\textbf{Pattern detection generality}}
     & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{XXX} \\
@@
     \hline
-    \multirow{4}{*}{Detected Pattern Types}
+    \multirow{4}{*}{\textbf{Detected Pattern Types}}
     & \multicolumn{1}{l}{Creational}  & \multicolumn{1}{l}{23} \\
@@
     \hline
-    \multirow{6}{*}{Validation Method}
+    \multirow{6}{*}{\textbf{Validation Method}}
     & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
@@
 
-%\begin{center}
-%  \includegraphics[scale=0.65]{pattern_types.png}
-%\end{center}
+\begin{center}
+  \includegraphics[scale=0.65]{pattern_types.png}
+\end{center}
 
@@
 The majority of techniques are language dependent and the most used 
-languages are Java and C++
-
-But those detection methods can be easily converted to other languages
+languages are Java and C++, but those detection methods can be easily converted to other languages
 just by modifying the font-end.
-
-%\begin{center}
-%\includegraphics[scale=0.75]{language_generality.png}
-%\end{center}
+\begin{center}
+	\includegraphics[scale=0.75]{language_generality.png}
+	\end{center}
 
@@
 
-%\begin{center}
-%\includegraphics[scale=0.75]{detection_level.png}
-%\end{center}
+\begin{center}
+\includegraphics[scale=0.75]{detection_level.png}
+\end{center}
 
@@
 
-%\begin{center}
-%\includegraphics[scale=0.75]{detection_generality.png}
-%\end{center}
+\begin{center}
+\includegraphics[scale=0.75]{detection_generality.png}
+\end{center}
 
@@
 
-%\begin{center}
-%\includegraphics[scale=0.75]{validation_method.png}
-%\end{center}
+Case studies are the most common methods with a weak rate of experiences and a total absence of true benchmarks, that's why researchers tend to use some gold standards and the most used one is JHotDraw due to the high quantity of design patterns detections tool that are developed in Java.
+We have also noticed that there is no validation standards, there is a lot of tools that can detect patterns, but since there are no standards 
+none of those tools can be truly reliable.
+All of these reasons can lead to a lack of maturity concerning design pattern detection.
+\begin{center}
+\includegraphics[scale=0.75]{validation_method.png}
+\end{center}
 
@@
 At first, we defined the detection level to be a disjoint classification category.
-However during the classification phase of our study, we stumbled upon unfoseen cases
+However during the classification phase of our study, we stumbled upon unforeseen cases
 where the detection was done at two levels. We had to change the classification

### 2016-01-01 article/data/analysis.py
Data analysis

@@ -1,0 +1,69 @@
+import pandas as pd
+import sys
+import math
+from fractions import gcd
+import itertools as it
+
+filename = "tm.csv"
+
+data = pd.read_csv(filename, quotechar='"', skipinitialspace=True)
+
+data_classification = data[data["Rejet"].isnull()]
+data_reject = data[data["Rejet"].notnull()]
+
+
+print "======================================================"
+print "Accepted for classification:\t" + str(len(data_classification))
+print "Rejected before classification:\t" + str(len(data_reject))
+print "======================================================"
+data = data_classification
+print "== Yearly distribution ==============================="
+for y in xrange(2000,2016):
+    print str(y) + ":\t\t" + str(len(data[data["Date publication"] == y]))
+print ""
+print "== Detection strategy ================================"
+print "Ai:\t\t"        + str(len(data[data["Ds-ai"].notnull()]))
+print "Logic:\t\t"     + str(len(data[data["Ds-logic"].notnull()]))
+print "Graph:\t\t"     + str(len(data[data["Ds-graph"].notnull()]))
+print "Metric:\t\t"    + str(len(data[data["Ds-metric"].notnull()]))
+print "Automata:\t"  + str(len(data[data["Ds-automaton"].notnull()]))
+print "Profiling:\t" + str(len(data[data["Ds-prof"].notnull()]))
+print "Matching:\t"  + str(len(data[data["Ds-matching"].notnull()]))
+print "Others:\t\t"    + str(len(data[data["Ds-other"].notnull()]))
+print ""
+print "== Language Dependance ==============================="
+print "Dependant:\t"    + str(len(data[data["Lg-dependant"].notnull()]))
+print "Independant:\t"  + str(len(data[data["Lg-independant"].notnull()]))
+print ""
+print "== Analysis Type ====================================="
+print "Static:\t\t"   + str(len(data[data["At-static"].notnull()]))
+print "Dynamic:\t"  + str(len(data[data["At-dynamic"].notnull()]))
+print "Hybrid:\t\t"   + str(len(data[data["At-hybrid"].notnull()]))
+print ""
+print "== Detection Level ==================================="
+print "Exec:\t\t"   + str(len(data[data["Dl-exec"].notnull()]))
+print "Source:\t\t" + str(len(data[data["Dl-source"].notnull()]))
+print "Model:\t\t"  + str(len(data[data["Dl-model"].notnull()]))
[…]

### 2016-01-01 article/main.tex
article

--- 2015-12-31 article/main.tex
@@
 \usepackage{multirow}
+%\usepackage[T1]{fontenc}
+%\usepackage[utf8]{inputenc}
 %\usepackage{epsfig} % for postscript graphics files
@@
 
-Design partterns are best pratices proposed by the Gang of Four in their seminal
-book to recurring design problems.
+Design partterns are best pratices to recurring design problems first proposed
+by the Gang of Four in their seminal book.
 
 (Some study author) have been able to show that the presence of design patterns,
-if correctly presented, can help one better understand a piece of software
-[citation needed].
-It is therefore desirable to be able to automatically extract those design
-and present them in a digestible format.
+if correctly presented, can help developpers better understand a piece of
+software [citation needed].
+It would therefore be desirable to be able to automatically extract those
+design patterns and present them in a digestible format.
 
@@
  The first section explains the systematic mapping process
- The second section analyses
+ The second section explains the selection process results
+ The third one deals analyses the study results
+ The article then continues with the limitations of our study
+ It finishes with related work.
 
@@
 in design pattern detection and the quality of proposed detection methods.
-% Our classification scheme doesn't really allow us to take any position
+% TODO: Our classification scheme doesn't really allow us to take any position
 % relative to the quality of the methods. At most, it provide a sensible
@@
 found on the subject.
-% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
-% doesn't make any sense.
+% TODO: Thesaurus is a synonym dictionnary... therefore a "disjunction of
+% thesaurus" makes no sense.
 To achieve that purpose we used for the query a disjonction of thesaurus for
@@
 The query was limitied to the abstract, the title, and keywords of each article.
-% Do we like oxford comma?
 
@@
 
-% This sentence is not necessary... It is evident that we excluded other domains.
+% TODO: This sentence is not necessary... It is evident that we excluded other
+% domains.
 We have also limited our research to the field of computer science and
@@
 
-% Problem with that sentence: "and process"?  Maybe "proceeded" 
+% TODO: Problem with that sentence: "and process"?  Maybe "proceeded" 
 After having queried the database, we exported the results found and process to
@@
     This criterion excludes articles where the main contribution is not about
-    design pattern as defined in by the Gang of Four ,
+    design pattern as defined in by the Gang of Four,
+    % TODO: We cannoct base our exclusion to DP defined by the GoF because we
+    % have a class for other pattern type.
+    % Limiting to software design patterns would be enough
   \item \textbf{The main contribution of the paper is not about a method of detecting design patterns}:
@@
 The inter-rater agreement Cohen's kappa gave us the following result:
-% citation needed
+% TODO: citation needed
 
 \begin{center}
-  \begin{tabular}{ lcc }
+  \begin{tabular}{ ccc }
     \bf Group & \bf \# of articles & \bf Cohen's kappa \\
-    \hline {}
+    \hline
     1 & ??? & 0.88 \\
@@
 It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
-a good agreeement.% citation needed
+a good agreeement. %TODO: citation needed
 
@@
     Possible values: Dependant or Independant
-% This  specifies if the detection is langage dependent or independent,
+% TODO: This  specifies if the detection is langage dependent or independent,
 
@@
 
-%todo
+%TODO
 
@@
 
-DATA
-
 \section{STUDY RESULTS}
 
+\subsection{Yearly distribution}
+% TODO: Need to change the title for this graphic
+
+The yearly distribution gives us an interesting picture of the field.
+Interest in design patterns detection technique started in the early
+2000 and that interest is fading away since 2010.
+
+This could indicate either that the field is mature and that research avenues
+have been exhaused, that the field currently hit a roadblock, or that interest
+is fading due to a lack of interest in the need for design pattern detection
+tools.
+
 \begin{center}
+\includegraphics[scale=0.7]{articles_by_years.png}
+\end{center}
+
+\subsection{Publication Venue Distribution}
+% TODO: Need a graphic for article by publishers.
+
+\begin{center}
+  \small
   \begin{tabular}{ lll }
@@
     \hline
-    multirow{3}{*}{Detection Level}
+    \multirow{3}{*}{Detection Level}
     & \multicolumn{1}{l}{Execution}    & \multicolumn{1}{l}{8} \\
@@
     \hline
-    \multirow{2}{*}{Pattern detection generality}
+    \multirow{2}{*}{Detection generality}
     & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{XXX} \\
@@
 \end{center}
-
-\subsection{Yearly distribution}
-% Need to change the title for this graphic
-
-The yearly distribution gives us an interesting picture of the field.
-Interest in design patterns detection technique started in the early
-2000 and that interest is fading away since 2010.
-
-This could indicate either that the field is mature and that research avenues
-have been exhaused, that the field currently hit a roadblock, or that interest
-is fading due to a lack of interest in the need for design pattern detection
-tools.
-
-\begin{center}
-\includegraphics[scale=0.75]{articles_by_years.png}
-\end{center}
-
-\subsection{Publication Venue Distribution}
-% Need a graphic for article by publishers.
 
@@
 \subsection{Language dependance}
+The main focus of this category was to identify the existance of language
+independant solutions to the detection of design patterns.
+
+To identify truly generic detection methods, proposed solutions requiring a
+frontend to implement have been classified as being dependant on the source
+language.
+
 The majority of techniques are language dependant and the most used 
@@
 just by modifying the font-end.
+
+Haotian and Shu[52] took a different approach by instrumenting Java bytecode
 
@@
 This category was used to expose specific pattern detection methods.
-Most papers present a general way to detect design patterns.
+As expected, papers tend to present detection method for detecting patterns
+in general.
+
+Some papers worth noting presents specifics ways to detect particular patterns.
+
+Marjan Heričko and Simon Beloglavec[355] presents a way of identifying
+composite design pattern, composite here corresponding to the composition of
+atomic DP (MVC).
+
+Ren and Zhao[80] used and hybrid analysis based on OWL, an ontology system,
+to recover instances candidates of Observer pattern followed by a dynamic
+analysis to accept or reject the recovered candidates.
 
@@
 \subsection{Classification}
+
+The distribution of articles between the reviewers may seem arbitrary in since it is not evenly distributed.
+In fact one reviewer had two less articles to read.
+This difference is due to an error when we compiled the articles that passed
+the screening phase where one article was featured twice.
+Since the remaining number of articles was not divisible by three, this same
+reviewer had already one less article to read.
+We believe this error has no effect on the overall result. \\
 

### 2016-01-01 article/main.tex
[fix] minor

--- 2015-12-31 article/main.tex
@@
 The main goal of this paper is to determine the quantity and trends of research
-in design pattern detection and the quality of proposed detection methods.
+in design pattern detection and the possibility of proposed detection methods.
 % Our classification scheme doesn't really allow us to take any position
@@
 % evaluation of the field
+
+% Pierre : oui par qualité je voulais dire ce qu'il est capable de detecter : possibility ?
 
@@
 % TODO: Original articles set <- better wording?!
+% Pierre "initial articles set " ?
 
@@
 % doesn't make any sense.
-To achieve that purpose we used for the query a disjunction of thesaurus for
+% Pierre : remplacé par "words with similar meanings"
+To achieve that purpose we used for the query a disjunction of words with similar meanings for
 \textit{detection} on their respective contracted form : \textit{detect*},
@@
 % Do we like oxford comma?
+% Pierre : je découvre ce que c'est, l'internet semble avoir un avis contreversé, il faut juste rester consistant.
 
@@
 % This sentence is not necessary... It is evident that we excluded other domains.
+% Pierre: Difficile à dire vu notre première critère d'exclusion après
 We have also limited our research to the field of computer science and
@@
 % Problem with that sentence: "and process"?  Maybe "proceeded" 
-After having queried the database, we exported the results found and process to
-screening.
+% Pierre : de fait
+After having queried the database, we exported the results found and proceeded to screening.
 
@@
 The inter-rater agreement Cohen's kappa gave us the following result:
-% citation needed
 
@@
 It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
-a good agreement.% citation needed
+a good agreement \cite{c3}.
 
@@
 
+\bibitem{c3} Landis, J. Richard, and Gary G. Koch. "The measurement of observer agreement for categorical data." biometrics (1977): 159-174.
+
 \end{thebibliography}

### 2016-01-01 article/main.tex

--- 2016-01-01 article/main.tex
@@
 Of those articles, we found two duplicates that were immediately removed from
-the set of articles to analyse which brings down the number of articles for
+the set of articles to analyze which brings down the number of articles for
 screening to 401.
+
+\begin{figure}
+ \centering
+  \begin{tabular}{ ccc }
+   \bf Group & \bf \# of articles & \bf Cohen's kappa \\
+   \hline {}
+   1 & 133 & 0.88 \\
+   2 & 133 & 0.66 \\
+   3 & 134 & 0.91 \\
+ \end{tabular}
+ \caption{Cohen's Kappa coefficients}
+\end{figure}
+
+\begin{figure*}[tb]
+ \centering
+ \includegraphics[scale=0.2]{flow.jpg}
+ \caption{Flow of information}
+\end{figure*}
 
@@
 
-The inter-rater agreement Cohen's kappa gave us the following result:
-% TODO: citation needed
-
-\begin{center}
-  \begin{tabular}{ ccc }
-    \bf Group & \bf \# of articles & \bf Cohen's kappa \\
-    \hline
-    1 & ??? & 0.88 \\
-    2 & ??? & 0.66 \\
-    3 & ??? & 0.91 \\
-  \end{tabular}
-\end{center}
+The inter-rater agreement Cohen's kappa gave us the following result presented
+in \textit{fig. 1}.
 
@@
     This determine the means on which the detection is based.
-    Possible values: Artificial intelligence, Logic/Formalisation, Graph,
+    Possible values: Artificial intelligence, Logic/Formalization, Graph,
     Metric, Automata, Instrumentation/profiling and Others.
 
-  \item \textbf{Language dependance}:
-    This category aims to classify detection methods on wether it is dependant
+  \item \textbf{Language dependence}:
+    This category aims to classify detection methods on whether it is dependent
     on the language or not. 
@@
 Interest in design patterns detection technique started in the early
-2000 and that interest is fading away since 2010.
+2000 and that interest plateaued between the years 2005 and 2013.
+Since then the field lost steam with a number of publication per years
+roughly equivalent to those at its inception.
 
@@
 \begin{center}
-\includegraphics[scale=0.7]{articles_by_years.png}
+ \begin{figure}
+  \includegraphics[scale=0.450]{year_distribution.png}
+  \caption{}
+ \end{figure}
 \end{center}
 
-\subsection{Publication Venue Distribution}
-% TODO: Need a graphic for article by publishers.
+%\begin{center}
+%\includegraphics[scale=0.7]{articles_by_years.png}
+%\end{center}
 
 \begin{center}
+  \begin{figure}
    \small
@@
     \hline
-    \multirow{7}{*}{Detection Srategy}
+    \multirow{7}{*}{Detection Strategy}
     & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
-    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{22} \\
-    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{15} \\
+    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{19} \\
+    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{13} \\
     & \multicolumn{1}{l}{Metric}       & \multicolumn{1}{l}{7} \\
     & \multicolumn{1}{l}{Automata}     & \multicolumn{1}{l}{1} \\
-    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{10} \\
-    & \multicolumn{1}{l}{Pattern Mathching}
+    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{9} \\
+    & \multicolumn{1}{l}{Pattern Matching}
                                        & \multicolumn{1}{l}{8} \\
-    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{23} \\
+    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{19} \\
     \hline
-    \multirow{2}{*}{\textbf{Language Dependance}}
-    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{XXX} \\
-    & \multicolumn{1}{l}{Independant}  & \multicolumn{1}{l}{XXX} \\
+    \multirow{2}{*}{\textbf{Language Dependence}}
+    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{37} \\
+    & \multicolumn{1}{l}{Independent}  & \multicolumn{1}{l}{16} \\
     \hline
     \multirow{3}{*}{\textbf{Analysis Type}}
-    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{XXX} \\
-    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{XXX} \\
-    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{25} \\
+    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{13} \\
+    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{17} \\
     \hline
@@
     & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\
-    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{7} \\
+    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{8} \\
     \hline
     \multirow{2}{*}{Detection generality}
-    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{XXX} \\
-    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{XXX} \\
+    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{40} \\
+    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{11} \\
     \hline
     \multirow{4}{*}{Detected Pattern Types}
-    & \multicolumn{1}{l}{Creationnal}  & \multicolumn{1}{l}{23} \\
-    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{34} \\
-    & \multicolumn{1}{l}{Behaviour}    & \multicolumn{1}{l}{49} \\
+    & \multicolumn{1}{l}{Creational}  & \multicolumn{1}{l}{22} \\
+    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{33} \\
+    & \multicolumn{1}{l}{Behavior}    & \multicolumn{1}{l}{37} \\
     & \multicolumn{1}{l}{Other/Not Specified}
-                                       & \multicolumn{1}{l}{17} \\
+                                       & \multicolumn{1}{l}{12} \\
     \hline
@@
     & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
-    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{40} \\
+    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{37} \\
     & \multicolumn{1}{l}{Experiment}   & \multicolumn{1}{l}{8} \\
@@
     & \multicolumn{1}{l}{Other}        & \multicolumn{1}{l}{1} \\
-    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{11}
+    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{8}
    \end{tabular}
+   \caption{Classification Results - Categories whose values represent disjoint sets are presented in bold}
+
+  \end{figure}
 \end{center}
+
+\subsection{Publication Venue Distribution}
+% Need a graphic for article by publishers.
 
@@
 Most of the detection strategies used fall either in the 
-\textit{logic/formalisation} or \textit{other} class.
+\textit{logic/formalization} or \textit{other} class.
 The first one was probably overly broad since it included any solution using
-inference rules engines, formalisation and semantic web ontologies.
+inference rules engines, formalization and semantic web ontologies.
 Surprisingly, the latter strategy was the focus of many articles.
+
+Another strong
 
@@
 Design pattern detection can be done either statically or dynamically.
+So
 
@@
 
-The Gang of Four identified three design pattern types: creationnal,
+The Gang of Four identified three design pattern types: creational,
 behavioural and structural patterns.
-Due to the nature of each pattern types, it is usally aknowledged that
-structural patterns should be easier to detect than behavioural patterns and
-that the later are easier than creationnal patterns (citation needed). 
+
+Due to the nature of each pattern types, our intuition would dictate that
+structural patterns should be easier to detect than behavioral patterns and
+that the later are easier than creational patterns (citation needed). 
 It was expected that this ordering would appear in the number of articles
 associated with each pattern types. 
-However, we can see that the detection of behavioural patterns has been the
+However, we can see that the detection of behavioral patterns has been the
 subject of more articles than the two others.
@@
 detection is considered as an easy problem, thus less likely to be the main
-focus of a research paper or by the possibility is that behavioural design
+focus of a research paper or by the possibility that behavioral design
 patterns are in fact easier to detect than structural ones.
-However, we believe the first possibilty to be more likely.
+We believe the first possibility to be more likely.
+
+Of interest is the relation between the type of analysis and the type of
+patterns detected. \textit{Fig. 5} and \textit{Fig. 6}
+respectively presents the distribution of the number of articles and the
+propotion.
+
+\begin{figure}
+ \centering
+ \begin{tabular}{llll}
+             & Static & Dynamic & Hybrid \\
+ \hline
+ Structural  & 18 & 7 & 8 \\
+ Behavioural & 17 & 7 & 13 \\
+ Creationnal & 14 & 1 & 7 \\
+ Other       & 3 & 5 & 4 \\
+ \end{tabular}
+ \caption{Analysis type according to detected pattern type}
+\end{figure}
+
+\begin{figure*}[tb]
+ \centering
+ \includegraphics[scale=0.7]{analysis_v_pattern.png}
+ \caption{Analysis type distribution per detected pattern type}
+\end{figure*}
 
@@
 
-The majority of techniques are language dependant and the most used 
-languages are Java and C++
-
-But those detection methods can be easily converted to other languages
+The majority of techniques are language dependent and the most used 
+languages are Java and C++, but those detection methods can be easily converted to other languages
 just by modifying the font-end.
@@
 
+Systems based on rules are examples of gendeals with an inference engine for which
+
 Some papers worth noting presents specifics ways to detect particular patterns.
 
-Marjan Heričko and Simon Beloglavec[355] presents a way of identifying
-composite design pattern, composite here corresponding to the composition of
-atomic DP (MVC).
+Heričko and Beloglavec[355] presents a way of identifying
+composite design pattern, not to be confused with the definition of the 
+composite pattern defined by the GoF, here composite pattern corresponds to the
+composition of atomic design pattern (the Model View Controler being an
+example of a composite pattern).
 
@@
 
+Case studies are the most common methods of validation with a weak rate of
+experiences and a total absence of true benchmarks.
+
+Researchers in the Java world seem to have agreed on the use of JHotDraw,
+JRefactory, JUnit, and AWT for evaluation.
+However, while JHotDraw, a software known for its internal use of design
+pattern, is the most frequently used, there is no clear benchmark.
+
+Very few articles have taken the time to do a proper comparative evaluation.
+De Lucia et al.[151] did an excellent work in that regard.
+They compared their approach to existing tools and P-MARt's knowledge base
+of pattern instances in JHotDraw and JRefactory, thus building a
+strong case for their technique.
+Unfortunately, most technique seem to be evaluated in a vacuum which makes it
+difficult to compare their efficiency.
+
+Also, because most technique are language dependant, comparative studies are
+often times limited to case study in one language.
+Again, few articles try to present results taken from software in written in
+different languages.
+This is problematic because no common ground for comparison exists between
+technique whose evaluation is done on software written in different languages.
+Gueheneux and Antoniol[255] presented an extensive evaluation of DeMIMA on
+five open source Java projects and 33 industrial component written in C++.
+While the use of closed source component is in itself problematic, the
+evaluation of their system on both Java and C++ programs is noteworthy.
+
+%TODO: citation needed
+Other articles, due to the work involved in manually identifying instances of
+design pattern for evaluation, have simply choosen to compare their result to
+the output of existing tools.
+Even if some use multiple tools to cross check the identified pattern instances,
+we believe such evaluation methods are flawed since we don't know how well
+those tools perform due to the absence of a standard benchmark.
+The existence of pattern repository like P-MARt should supersede those
+validation technique.
+
+We have also noticed that there is no validation standards, there is a lot
+of tools that can detect patterns, but since there are no standards 
+none of those tools can be truly reliable.
+
+All these issues seem to indicate a lack of maturity of the field of design
+pattern detection.
+At least, more work is needed compare the different techniques.
+
 %\begin{center}
@@
 %\end{center}
-
-\subsection{Detected pattern types according to analysis type}
-% Need graphics
 
@@
 reviewer had already one less article to read.
-We believe this error has no effect on the overall result. \\
+We believe this error has no effect on the overall result.
 
-At first, we defined the detection level to be a disjoint classification category.
-However during the classification phase of our study, we stumbled upon unfoseen cases
-where the detection was done at two levels. We had to change the classification
-scheme to allow those cases.
+At first, we defined the detection level to be a disjoint classification
+category.
+However during the classification phase of our study, we stumbled upon
+unforeseen cases where the detection was done at two levels.
+We had to change the classification scheme to allow those cases.
 
@@
 
-So far, no other comparable studies has been done on the field of design pattern
-recognition.
+While no other systematic mapping study have been done on design pattern
+detection technique, other reseachers attempted to address the problems
+present in the field.
 
-(article on method validation) have identified a problem in the evaluation of design
-pattern detection methods. This problem has been observed in our evaluation of the
-domain in that most articles evaluates their algorithms with case studies that are
-hardly comparable.
+Pettersson, Lowe, and Nivre[190] identified a lack of proper evaluation of 
+design pattern detection technique, in part due to the absence of an accepted
+standard benchmark.
+This problem has been observed in our evaluation of the domain in that most
+articles evaluates their algorithms with case studies that are hardly
+comparable.
+They identified the existance of evaluation gold standard in JHotDraw, Swing
+and AWT  and pushed for the definition of a standard benchmark made of varied
+systems (language, size, etc.)
 

### 2016-01-01 article/main.tex

@@
 The main goal of this paper is to determine the quantity and trends of research
-in design pattern detection and the quality of proposed detection methods.
-% TODO: Our classification scheme doesn't really allow us to take any position
+in design pattern detection and the possibility of proposed detection methods.
+% Our classification scheme doesn't really allow us to take any position
 % relative to the quality of the methods. At most, it provide a sensible
 % evaluation of the field
+
+% Pierre : oui par qualité je voulais dire ce qu'il est capable de detecter : possibility ?
 
@@
 found on the subject.
-% TODO: Thesaurus is a synonym dictionnary... therefore a "disjunction of
-% thesaurus" makes no sense.
-To achieve that purpose we used for the query a disjonction of thesaurus for
+% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
+% doesn't make any sense.
+% Pierre : remplacé par "words with similar meanings"
+To achieve that purpose we used for the query a disjunction of synonyms for
 \textit{detection} on their respective contracted form : \textit{detect*},
 \textit{recogni*} and \textit{ident*}.
-We have then added to the query a disjonction of \textit{pattern} and \textit{motif}.
-The query was limitied to the abstract, the title, and keywords of each article.
+We have then added to the query a disjunction of \textit{pattern} and \textit{motif}.
+The query was limited to the abstract, the title, and keywords of each article.
+% Do we like oxford comma?
+% Pierre : je découvre ce que c'est, l'internet semble avoir un avis contreversé, il faut juste rester consistant.
 
@@
 % domains.
+% Pierre: Difficile à dire vu notre première critère d'exclusion après
 We have also limited our research to the field of computer science and
@@
  \centering
- \includegraphics[scale=0.2]{flow.jpg}
+ \includegraphics[scale=0.5]{flow.png}
  \caption{Flow of information}
@@
 
-% TODO: Problem with that sentence: "and process"?  Maybe "proceeded" 
-After having queried the database, we exported the results found and process to
-screening.
+After having queried the database, we exported the results found and proceeded to screening.
 
@@
 It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
-a good agreeement. %TODO: citation needed
+a good agreement \cite{c3}.
 
@@
 \subsection{Yearly distribution}
-% TODO: Need to change the title for this graphic
 
@@
     \multirow{3}{*}{Detection Level}
-    & \multicolumn{1}{l}{Execution}    & \multicolumn{1}{l}{8} \\
     & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\

### 2016-01-02 article/main.tex
changes

@@
 publishers search engines that do not provide an export functionality.
-Consequently, Scopus was used mostly as a Search and Export portal over the
+Consequently, Scopus was used as a mostly as a search and export portal over the
 relevant publications, greatly reducing the effort needed to extract the
-original articles set. 
-% TODO: Original articles set <- better wording?!
-% Pierre "initial articles set " ?
+initial articles set.
 
@@
 found on the subject.
-% Thesaurus is a synonym dictionnary... therefore a "disjunction of thesaurus"
-% doesn't make any sense.
-% Pierre : remplacé par "words with similar meanings"
-To achieve that purpose we used for the query a disjunction of synonyms for
-\textit{detection} on their respective contracted form : \textit{detect*},
-\textit{recogni*} and \textit{ident*}.
-We have then added to the query a disjunction of \textit{pattern} and \textit{motif}.
-The query was limited to the abstract, the title, and keywords of each article.
-% Do we like oxford comma?
-% Pierre : je découvre ce que c'est, l'internet semble avoir un avis contreversé, il faut juste rester consistant.
+It was decided to run our query only on the title, the abstract and the keywords of
+each article. 
+Our query was relatively simple,  "design pattern" and "detection" had to be present
+in the searched part of an article.
+To maximize the number of publications found, we considered variations of both part
+of our query in the form of synonyms and words sharing the same root.
+Therefore, we have extended our query to not only match "design pattern" but "design motif" as well. In the same vein, instead of only "detection" and its variations
+"identification" and "recognition", we queried their contracted forms "detect*",
+"ident*", and "recogni*".
 
@@
 
-% TODO: This sentence is not necessary... It is evident that we excluded other
-% domains.
-% Pierre: Difficile à dire vu notre première critère d'exclusion après
 We have also limited our research to the field of computer science and
@@
 
-The query resulted in a total of 403 articles.
-Of those articles, we found two duplicates that were immediately removed from
-the set of articles to analyze which brings down the number of articles for
-screening to 401.
-
-\begin{figure}
- \centering
-  \begin{tabular}{ ccc }
-   \bf Group & \bf \# of articles & \bf Cohen's kappa \\
-   \hline {}
-   1 & 133 & 0.88 \\
-   2 & 133 & 0.66 \\
-   3 & 134 & 0.91 \\
- \end{tabular}
- \caption{Cohen's Kappa coefficients}
-\end{figure}
-
-\begin{figure*}[tb]
- \centering
- \includegraphics[scale=0.5]{flow.png}
- \caption{Flow of information}
-\end{figure*}
-
 \subsection{Screening}
-
-After having queried the database, we exported the results found and proceeded to screening.
-
-This process was done by pair.
-For each article, we check that the result was the same for each individual in
-the pair.
-In the case of difference, we first talk about it to find common ground, then
-if the conflict was not resolved, we asked a senior researcher for a final
-decision.
 
@@
     reports.
-  \item \textbf{Not a full conference or research paper},
-    This criterion was used to exclude small
-  \item \textbf{Not about software design pattern}:
+  \item \textbf{Not a full conference or research paper}:
+    This criterion was used to exclude small research papers
+  \item \textbf{Not about software design patterns}:
     This criterion excludes articles where the main contribution is not about
-    design pattern as defined in by the Gang of Four,
+    software design patterns,
     % TODO: We cannoct base our exclusion to DP defined by the GoF because we
@@
 
-If in article matched more than one criteria, we assigned the lowest criteria
-to it.
-
-We were three author to work on the screening, we therefore created three pair
-of author including on average 135 articles per pair.
-
-The inter-rater agreement Cohen's kappa gave us the following result presented
-in \textit{fig. 1}.
-
-It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
-a good agreement \cite{c3}.
+The rejection criteria are ordered: an article that doesn't satisfy a specific
+criteron cannot be rejected for a succeeding one.
+Hence, the lowest applicable exclution criteron should always be the cause of
+rejection.
 
@@
 \subsection{Systematic map}
-
-%TODO
+The systematic mapping
 
 \section{SELECTION PROCESS RESULTS}
+
+\textit{Fig. 1} illustrates the flow of information at each phase of the study.
+
+\subsection{Selection}
+
+As per the systematic mapping study process, we started with a sizeable initial
+article set, reducing its size at each phase as not relevant articles were rejected.
+
+Our initial article set was made of 403 articles returned by the query on Scopus
+database.
+
+Of those articles, we found two duplicates that were immediately removed from
+the set of articles to analyze, which brought down the number of articles for
+screening to 401.
+
+\subsection{Screening}
+
+After having queried the database and removed the duplicates, we exported the
+results found as a .csv file and proceeded to screening.
+
+As we were three authors to work on the screening, we created three pairs
+of evaluators and distributed the articles evenly between them.
+
+The screening phase was done with the help of a spreadsheet where a column was
+created for each evaluator.
+Each evaluator was intructed to rate each article he's been assigned with a number
+from 1 to 5, where 5 corresponds to the acceptation of the article and numbers below
+to the applicable rejection criteron as defined in the previous section.
+To prevent the rejection of relevant article, raters were instructed to accept
+any article susceptible of being relevant with the afterthought that it could be
+rejected after a complete reading.
+
+Each article was rated according to the reading of its title and its abstract by
+individual evaluator.
+
+\begin{figure*}[tb]
+ \centering
+ \includegraphics[scale=0.5]{flow.png}
+ \caption{Flow of information}
+\end{figure*}
+
+\begin{figure}
+ \centering
+  \begin{tabular}{ ccc }
+   \bf Group & \bf \# of articles & \bf Cohen's kappa \\
+   \hline {}
+   1 & 132 & 0.88 \\
+   2 & 133 & 0.66 \\
+   3 & 134 & 0.91 \\
+ \end{tabular}
+ \caption{Cohen's Kappa coefficients}
+\end{figure}
+
+For each article, we ensured that articles were rated consistently amongst the
+evaluators.
+
+Disagreement in the rating of article inside a pair were firstly dealt with a
+reconsidaration of the rating of each individual according to the arguments of his opposing rater.
+In the case of unresolved disagreement, we brought our case before a senior
+researcher that published in the studied field who would instruct us over the final
+decision.
+If even he could settle de disagreement, the article was included to possibly be
+excluded at a later point.
+
+\subsubsection{Cohen's kappa coefficient}
+We calculated inter-rater agreement Cohen's kappa coefficient over the
+rejection and acceptation of each articles, which gaves us an average coefficient
+of 0.82.
+Individual results for each pair of evaluators is given in \textit{Fig. 2}
+alongside the number of articles assigned to each one.
+
+It is usually said that a Cohen's kappa coefficient of more than $0.7$ indicate
+a good agreement \cite{c3}.
+
+\subsection{Classification}
 
@@
 
-\begin{center}
 \begin{figure}
+  \centering
   \includegraphics[scale=0.450]{year_distribution.png}
@@
 \end{figure}
-\end{center}
 
-%\begin{center}
-%\includegraphics[scale=0.7]{articles_by_years.png}
-%\end{center}
-
-\begin{center}
 \begin{figure}
+  \centering
    \small
@@
 \end{figure}
-\end{center}
 
@@
 
-%\begin{center}
-%\includegraphics[scale=0.75]{detection_strategy.png}
-%\end{center}
-
 \subsection{Analysis Type}
@@
 So
-
-%\begin{center}
-%\includegraphics[scale=0.75]{analysis_type.png}
-%\end{center}
 
@@
 subject of more articles than the two others.
-
-%\begin{center}
-%  \includegraphics[scale=0.65]{pattern_types.png}
-%\end{center}
 
@@
 
-%\begin{center}
-%\includegraphics[scale=0.75]{language_generality.png}
-%\end{center}
-
 \subsection{Detection Level}
@@
 be done on multiple levels.
-
-%\begin{center}
-%\includegraphics[scale=0.75]{detection_level.png}
-%\end{center}
 
@@
 composite design pattern, not to be confused with the definition of the 
-composite pattern defined by the GoF, here composite pattern corresponds to the
-composition of atomic design pattern (the Model View Controler being an
+composite pattern defined by the GoF, here, composite pattern corresponds to the
+composition of atomic design pattern (the Model View Controler pattern being an
 example of a composite pattern).
@@
 analysis to accept or reject the recovered candidates.
-
-%\begin{center}
-%\includegraphics[scale=0.75]{detection_generality.png}
-%\end{center}
 
@@
 often times limited to case study in one language.
-Again, few articles try to present results taken from software in written in
+Again, few articles try to present results taken from software written in
 different languages.
@@
 five open source Java projects and 33 industrial component written in C++.
-While the use of closed source component is in itself problematic, the
+While the use of closed source components is in itself problematic, the
 evaluation of their system on both Java and C++ programs is noteworthy.
@@
 the output of existing tools.
-Even if some use multiple tools to cross check the identified pattern instances,
+Even if some use multiple tools to cross-check the identified pattern instances,
 we believe such evaluation methods are flawed since we don't know how well
@@
 The existence of pattern repository like P-MARt should supersede those
-validation technique.
+validation techniques.
 
@@
 pattern detection.
-At least, more work is needed compare the different techniques.
+At least, more work is necessary to compare the different techniques.
 

### 2016-01-02 article/main.tex
[fix] typo

@@
 Disagreement in the rating of article inside a pair were firstly dealt with a
-reconsidaration of the rating of each individual according to the arguments of his opposing rater.
+reconsideration of the rating of each individual according to the arguments of his opposing rater.
 In the case of unresolved disagreement, we brought our case before a senior

### 2016-01-02 article/main.tex
[fix] typo

@@
 created for each evaluator.
-Each evaluator was intructed to rate each article he's been assigned with a number
+Each evaluator was instructed to rate each article he's been assigned with a number
 from 1 to 5, where 5 corresponds to the acceptation of the article and numbers below
-to the applicable rejection criteron as defined in the previous section.
+to the applicable rejection criterion as defined in the previous section.
 To prevent the rejection of relevant article, raters were instructed to accept

### 2016-01-02 article/main.tex
so far

--- 2016-01-02 article/main.tex
@@
 After having queried the database and removed the duplicates, we exported the
-results found as a .csv file and proceeded to screening.
+results found as a .csv file and proceeded to the screening.
 
@@
    2 & 133 & 0.66 \\
-   3 & 134 & 0.91 \\
+   3 & 133 & 0.91 \\
  \end{tabular}
@@
 Disagreement in the rating of article inside a pair were firstly dealt with a
-reconsideration of the rating of each individual according to the arguments of his opposing rater.
+reconsidaration of the rating by each individual according to the arguments of
+his opposing rater.
 In the case of unresolved disagreement, we brought our case before a senior
@@
 decision.
-If even he could settle de disagreement, the article was included to possibly be
+If even he couldn't settle de disagreement, the article was included to possibly be
 excluded at a later point.
 
+94 articles passed our exclusion scheme and thus the screening phase.
+
 \subsubsection{Cohen's kappa coefficient}
+Cohen's kappa coefficient is a measure of the inter-agreement between two rater
+over the classification of a set of values.
+A high coefficient value is indicative of a relative agreement between a pair
+of raters.
+
 We calculated inter-rater agreement Cohen's kappa coefficient over the
-rejection and acceptation of each articles, which gaves us an average coefficient
-of 0.82.
+rejection and acceptation of each articles, which gaves us an average
+coefficient of 0.81.
 Individual results for each pair of evaluators is given in \textit{Fig. 2}
@@
 \subsection{Classification}
+
+Considering the number of articles that passed the screening phase
 
@@
 
-Design pattern detection can be done either statically or dynamically.
-So
+Design pattern detection can be done either statically, dynamically or in
+a combination of both.
+
+A little bit less than half of the articles favoured a static approach to the
+recognition of design motifs.
 
@@
 patterns detected. \textit{Fig. 5} and \textit{Fig. 6}
-respectively presents the distribution of the number of articles and the
-propotion.
+respectively presents the distribution of the number of articles and their
+proportion in this relation.
 
@@
 The majority of techniques are language dependent and the most used 
-languages are Java and C++, but those detection methods can be easily converted to other languages
-just by modifying the font-end.
-
-Haotian and Shu[52] took a different approach by instrumenting Java bytecode
+languages are Java and C++, but those detection methods can be easily converted
+to other languages by a simple modification of a font-end.
 
 \subsection{Detection Level}
+
 We found out that almost all of design patterns detection methods 
-identify the patterns on a source code level, though, the detection could
+identify the patterns at the source code level, though, the detection could
 be done on multiple levels.
+
+When detection was done at multiple level, more often than not it was at both
+the source and execution level.
 
@@
 
-Systems based on rules are examples of gendeals with an inference engine for which
+Systems based on rules are examples of general technique for which 
+an inference engine is able to handle any patterns it has a rule for.
+Di Martino and Esposito[40] presented a technique where ODOL is used
+to describe the structural aspects of patterns.
 
@@
 
-%\begin{center}
-%\includegraphics[scale=0.75]{validation_method.png}
-%\end{center}
-
 \section{Study limitations}
@@
 To mitigate the possibility of missing relevant articles we made sure that
-Scopus indexes the big venues of software engineering (ACM, Springer, IEEE, and
-???).
+Scopus indexes the big venues of software engineering (ACM, Springer and IEEE).
 
@@
 screening level due to a non representative title and abstract.
-We believe the possibility to be unlikely since each article were screened by
+We believe the possibility to be unlikely since each article was screened by
 two reviewers and that if the article had a possibly misleading title, it would

### 2016-01-02 article/main.tex
modified:   main.tex

@@
 
-A conclusion section
+In this paper we conducted a systematic mapping study to get an overview on existing research on design pattern detection.
+We queried Scopus database that indexes multiple sources (IEEE,ACM,SPRINGER and other) and we identified 55 article between 2000 and 2015 that are relevant to our study.
+We collected all the articles after querying the database, then we screened them using their title, abstract and keywords to ensure that they were relevant to our work.
+Finally we analyzed every one of the included article to classify them according to our classification scheme.
+Interest on the detection of design pattern has been growing increasingly since 2003, but the field began to lose its interest after 2010.
+In response to RQ1, the filed of design pattern detection still suffers from a lack of maturity 
+(Section IV J) and it's clear that the domain  still has some way to go, to reach the necessary maturity.
+It would be interesting to have more experiments and real benchmarks to help  standardizing and evaluating design pattern detection tools.
 

### 2016-01-02 article/main.tex
so long and thanks for all the fish

--- 2016-01-02 article/main.tex
@@
 
+For the classification phase, we distributed the 94 articles evenly among the
+three evaluators.
+Each article has been read thoroughly and classified according to the
+classification scheme if considered relevant to the study.
+
+Misleading articles that passed screening phase were removed at that point.
+A total of 39 articles have been rejected in this fashion.
+
 \section{STUDY RESULTS}
@@
 \subsection{Publication Venue Distribution}
+% Need a graphic for article by publishers.
+
+\subsection{Publication type distribution}
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.40]{doctype.png}
+  \caption{Distribution of papers by type of document}
+\end{figure}
+
 % Need a graphic for article by publishers.

### 2016-01-02 article/data/analysis.py
so far

@@ -9,6 +9,7 @@ import itertools as it
 filename = "tm.csv"
 
 data = pd.read_csv(filename, quotechar='"', skipinitialspace=True)
+scopus = pd.read_csv("scopus2.csv", quotechar='"', skipinitialspace=True)
 
 data_classification = data[data["Rejet"].isnull()]
 data_reject = data[data["Rejet"].notnull()]
@@ -19,10 +20,23 @@ print "Accepted for classification:\t" + str(len(data_classification))
 print "Rejected before classification:\t" + str(len(data_reject))
 print "======================================================"
 data = data_classification
+r = pd.merge(data, scopus, on="Article", how="inner")
+
 print "== Yearly distribution ==============================="
 for y in xrange(2000,2016):
     print str(y) + ":\t\t" + str(len(data[data["Date publication"] == y]))
 print ""
+print "== Document type ====================================="
+a=len(r[r["Document Type"] == "Article"])
+b=len(r[r["Document Type"] == "Conference Paper"])
+c=len(r[r["Document Type"].apply(lambda x: "workshop" in x or "Workshop" in x)])
+print "Article:\t\t" + str(a)
+print "Conference paper:\t" + str(b) 
+print "Workshop:\t" + str(c)
+print "Proceedings:\t" + str(55 - a - b - c)
+
+
+
 print "== Detection strategy ================================"
 print "Ai:\t\t"        + str(len(data[data["Ds-ai"].notnull()]))
 print "Logic:\t\t"     + str(len(data[data["Ds-logic"].notnull()]))
@@ -91,6 +105,64 @@ print "Other:\t\t"     + str(os) + "\t" +  str(od) + "\t" + str(oh)
 plt.hist(data["Date publication"], facecolor="grey")
 plt.title("Distribution of articles over the years")
 plt.savefig("../img/year_distribution.png")
+
+# Document type
+
+fig = plt.figure(figsize=(8,4))
+gs1 = GridSpec(1, 2)
+p1 = fig.add_subplot(gs1[0])
+p2 = fig.add_subplot(gs1[1])
+
+p1.pie([a,b,c, 55 - a - b- c], autopct='%1.1f%%', pctdistance=1.2, colors=
+["lightgrey", "grey", "darkgrey", "black"])
+p1.axis("equal")
+
[…]

### 2016-01-02 article/main.tex
so far
lol

@@
 
-Considering the number of articles that passed the screening phase
-
 For the classification phase, we distributed the 94 articles evenly among the
@@
 Each article has been read thoroughly and classified according to the
-classification scheme if considered relevant to the study.
+classification scheme by individual reviewers if considered relevant to the
+study.
 
 Misleading articles that passed screening phase were removed at that point.
-A total of 39 articles have been rejected in this fashion.
+A total of 39 articles have been rejected in this fashion leaving a total of
+55 articles relevant to our study
+
+The resulting classification and interpretation will be discussed in the next
+section.
 
 \section{STUDY RESULTS}
+
+In this section, the article will analyse different measures obtained from
+the final set of articles.
+More precisely, the article will look at the yearly distribution, the publisher
+distribution, the publication type distribution and each category define
+earlier in the classification scheme.
 
@@
   \caption{}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.40]{publisher.png}
+  \caption{Distribution of papers by publishers}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.40]{doctype.png}
+  \caption{Distribution of papers by type of document}
 \end{figure}
@@
 
-\subsection{Publication Venue Distribution}
-% Need a graphic for article by publishers.
+\subsection{Publishers Distribution}
+
+\textit{Fig. 4} shows a partial distribution of the articles between their
+resspective publishers. 
+In many cases, data exported from Scopus is lacking the publisher which
+resulted in the classification of many articles as \textit{Other}.
+Manual inspection would be required.
 
 \subsection{Publication type distribution}
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.40]{doctype.png}
-  \caption{Distribution of papers by type of document}
-\end{figure}
 
-% Need a graphic for article by publishers.
+\textit{Fig. 5} shows the distribution of the papers according to their
+types.
+Unsurprisingly, half of them are conference paper, while a third are journal
+articles.
 
@@
 Of interest is the relation between the type of analysis and the type of
-patterns detected. \textit{Fig. 5} and \textit{Fig. 6}
+patterns detected. \textit{Fig. 7} and \textit{Fig. 8}
 respectively presents the distribution of the number of articles and their

### 2016-01-02 article/main.tex
Jsuis tanné

@@
 
+Choosing a specific type of analysis tels a lot about the associated technique.
+Static analysis is useful when trying to extract structural and semantic
+information about a program while dynamic analysis makes it easier to get
+information about the behaviour of an algorithm.
+
+The analysis type also affect the kind of tool the algorithm is implemented
+in.
+In fact dynamic analysis requires much more processing time due to the
+profiling aspect associated with it.
+This effectively prevent the inclusion of detection algorithm as a realtime
+programing aid.
+
 A little bit less than half of the articles favoured a static approach to the
-recognition of design motifs.
+recognition of design motifs, while the other half had a dynamic aspect to
+their detection methods.
 
@@
 \end{figure*}
+
+For structural patterns, a static analysis can be said to be efficient enough.
+More than half the detection method used such an analysis with good results
+
+For behavioural pattern, static analysis migh be sufficient but a majority of
+article includes a dynamic component to the anaylis.
+Tsantalis et al.[325] had good result with their graph similarity scoring
+approach for detecting structural and behavioural pattern with a static method.
+
+Creationnal patterns show an interesting distribution of the analysis types.
+In fact, it could be said that their identification is difficult with
+ a dynamic analysis alone.
+Strangely though, a high proportion of article report the recognition of
+creationnal design patterns with only a static analysis.
 

### 2016-01-02 article/main.tex
modified:   main.tex

--- 2016-01-02 article/main.tex
@@
 
-Design partterns are best pratices to recurring design problems first proposed
-by the Gang of Four in their seminal book.
+Design patterns are best practices to recurring design problems, first it was proposed by the Gang of Four in their seminal book.
 
 (Some study author) have been able to show that the presence of design patterns,
-if correctly presented, can help developpers better understand a piece of
+if correctly presented, can help developers better understand a piece of
 software [citation needed].
@@
 Proposed methods of automatic detection aims in part to facilitate the work of
-developers in understanding a piece of software through reverse engineering.
+developers in understanding a piece of software through reverse engineering and facilitate work during maintenance.
 
@@
 No studies have been conducted to analyze the trends of the field.
+
+Systematic mapping is a relatively new research method in software
+engineering, adapted from other disciplines by Kitchenham
+[5]. It is an alternative to systematic reviews and could be used if
+the amount of empirical evidence is too little, or if the topic is too
+broad, for a systematic review to be feasible. A mapping study is performed
+at a higher granularity level with the aim to identify research
+gaps and clusters of evidence in order to direct future research.
+Petersen et al. [1] describe how to conduct
+a systematic mapping study in software engineering. Our study
+is conducted in accordance with these guidelines and 
+we have introduced a classification scheme specific to our topic.
 
@@
 
-For the classification phase, we distributed the 94 articles evenly among the
-three evaluators.
-Each article has been read thoroughly and classified according to the
-classification scheme if considered relevant to the study.
-
-Misleading articles that passed screening phase were removed at that point.
-A total of 39 articles have been rejected in this fashion.
-
 \section{STUDY RESULTS}
@@
 \subsection{Publication Venue Distribution}
-% Need a graphic for article by publishers.
-
-\subsection{Publication type distribution}
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.40]{doctype.png}
-  \caption{Distribution of papers by type of document}
-\end{figure}
-
 % Need a graphic for article by publishers.
@@
 
-\bibitem{c2} www.scopus.com
+\bibitem{c2} Landis, J. Richard, and Gary G. Koch. "The measurement of observer agreement for categorical data." biometrics (1977): 159-174.
 
-\bibitem{c3} Landis, J. Richard, and Gary G. Koch. "The measurement of observer agreement for categorical data." biometrics (1977): 159-174.
+\bibitem{C3} D. Yu, Y. Zhang and Z. Chen. "A comprehensive approach to the recovery of design pattern instances based on sub-patterns and method signatures" 2015, Journal of Systems and Software
+
+\bibitem{C4} O. Kaczor, Y. Guéhéneuc and S. Hamel "Identification of design motifs with pattern matching algorithms" 2010, Information and Software Technology
+
+\bibitem{C5} B.A. Kitchenham, Guidelines for performing systematic literature reviews in
+software engineering version 2.3, Technical Report S.o.C.S.a.M. Software
+Engineering Group, Keele University and Department of Computer Science
+University of Durham, 2007.
+
+\bibitem{C6} Tsantalis, N. Chatzigeorgiou, A. Stephanides, G. 
+Halkidis, S.T., "Design pattern detection using similarity scoring" 2006, IEEE Transactions on Software Engineering
+
+\bibitem{C7}
+
+\bibitem{c3} www.scopus.com
 

### 2016-01-02 article/main.tex
lol
almost

@@
 It is organized as follows: 
- The first section explains the systematic mapping process
- The second section explains the selection process results
- The third one deals analyses the study results
- The article then continues with the limitations of our study
- It finishes with related work.
+ the first section explains the systematic mapping process,
+ the second section explains the selection process results,
+ the third one deals analyses the study results,
+ the article then continues with the limitations of our study,
+ and it concludes with related works.
 
@@
 
-Another strong
+Another big avenue for detection strategy lies in artificial intelligence
+and machine learning.
+In fact, a fifth of the articles make use an AI technique.
+
+Graph methods are popular popular and half the time have been used jointly with
+pattern matching techniques.
 
@@
 article includes a dynamic component to the anaylis.
-Tsantalis et al.[325] had good result with their graph similarity scoring
+Tsantalis et al.\cite{6} had good result with their graph similarity scoring
 approach for detecting structural and behavioural pattern with a static method.
+
+Kaczor et al.\cite{4} use an hybrid graph matching algorithm to detect creationnal
+and structural design pattern.
 
